Transferring Value Functions by Variational Methods

### 2018-05-17 NIPS 2018/main.tex
Minor changes to Related Works

\begin{abstract}
We consider the problem of transferring value functions in reinforcement learning. We propose an approach that uses the given source tasks to learn a prior distribution over optimal value functions and provide an efficient variational approximation of the corresponding posterior in a new target task. We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures. We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.\todo{Say something more about the advantages of our method}
\end{abstract}

@@

%\subsection{Variational Inference}
%
%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^d$ given data $D$,
%\begin{equation}\label{eq:bayes}
%p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
%\end{equation}
%is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq. \eqref{eq:bayes}. The main intuition behind variational inference~\cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$. The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t. $p$:
%\begin{equation}
%\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
%\end{equation}
%It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
%\begin{equation}
%\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
%\end{equation}
%Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.

@@

Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve. Then, we can compute the posterior distribution over weights given such dataset by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$. Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$. In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions to get tractable posteriors. However, in our transfer settings, all distributions involved depend on the family of tasks under consideration and making such assumptions is likely to limit the applicability to specific problems. Thus, we take a different approach to derive a more general, but still well-grounded, solution. Recall that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$. Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
\begin{equation}\label{eq:gibbs}
q(\bm{w}) = \frac{e^{-\Lambda\norm{B_{\bm{w}}}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B_{\bm{w}'}}_D^2}p(d\bm{w}')},
\end{equation}
for some parameter $\Lambda > 0$. \todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$. Notice that, whenever the term $e^{-\Lambda\norm{B_{\bm{w}}}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior. Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models. Thus, we propose a variational approximation $q_{\bm{\xi}}$ by considering a simpler family of distributions parameterized by $\bm{\xi} \in \Xi$. Then, our problem reduces to finding the variational parameters $\bm{\xi}$ such that $q_{\bm{\xi}}$ minimizes the Kullback-Leibler (KL) divergence w.r.t. the Gibbs posterior $q$. From the theory of variational inference (e.g., \cite{blei2017variational}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
\begin{align} \label{eq:elbo}
\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
\end{align}
The approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term). Assuming that we can compute the gradients of \eqref{eq:elbo} w.r.t. the variational parameters $\bm{\xi}$, our objective can be optimized using any stochastic optimization algorithm, as shown in the next subsections.

@@

We now restrict to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement. We assume that optimal $Q$-functions (or better, their weights) follow a multivariate Gaussian distribution. That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite). Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^d, \bm{\Sigma}\in\mathbb{R}^{d\times d}, \bm{\Sigma}\succ 0 \right\}$. To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead. In this case, deriving the gradient of the objective is very simple. Both the KL between two multivariate Gaussians and its gradients have a simple closed-form expression. The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}). Although these results are well-known in the literature, we report them in App. \ref{} to have a more self-contained description.

@@

From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t. $\bm{\xi}$ requires differentiating $\norm{B_{\bm{w}}}_D^2$ w.r.t. $\bm{w}$. Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator. This issue rarely is a problem since typical value-based algorithms are semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}). However, our transfer settings are quite different from common RL. In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum and aims only to adapt the weights in some direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the target task. Unfortunately, this property does not hold for most semi-gradient algorithms. Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching an optimum, and require many tricks and tuning to work well \cite{schaul2015prioritized,van2016deep}. This property is clearly undesirable in our case, as we only aim at adapting already good solutions. Thus, we consider using a residual gradient algorithm \cite{baird1995residual}. To differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
\begin{equation}
\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
\end{equation}
where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions. The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}. Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t. the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}_{\bm{w}}}_D^2$, is now differentiable w.r.t. $\bm{w}$. Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart. \cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence. This projection is obtained by including a parameter $\psi\in[0,1]$ in the TD error gradient:
\begin{equation}
\nabla_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right),
\end{equation}
where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$. Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$). A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee convergence).

@@

Our approach is mostly related to \cite{lazaric2010bayesian}. Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions. In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks. Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it. However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability. On the contrary, our approach can handle high-dimensional tasks. In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks. Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, so as to obtain a more scalable approach.\todo{More comments about HiP-MDPs? Should we discuss more related works?}

@@

\subsection{Proof of Theorem 2}

@@

Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$. Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}. Thus, we can write:

@@

\pi_{\beta_{\kappa}}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}

@@

\subsection{Proof of Theorem 3}

We begin by proving some important lemmas. Then, we use them to derive a finite-sample analysis of Alg. \ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm. \ref{th:main-gaussian}) and Gaussian mixture models (Thm. \ref{th:main-mixture}).

\begin{lemma}\label{lemma:l1}
Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively. Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$. Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
\begin{equation}
\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
\end{equation}
\end{lemma}
\begin{proof}
First notice that:
\begin{align*}
\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} + TQ_{\bm{w}} - TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
\end{align*}
which implies that:
\begin{align*}
\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2
\end{align*}
Then we can write:
\begin{align*}
P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
\end{align*}
Settings the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
\end{proof}

Lemma \ref{lemma:l1} can be straightforwardly extended to the case where the mellow Bellman operator is used instead of the optimal one. This is given in the following corollary.

\begin{corollary}\label{cor:diff-q}
Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively. Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$. Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
\begin{equation}
\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
\end{equation}
\end{corollary}

We now prove some important properties of the variational approximation introduced in Sec. \ref{sec:alg}. Our results generalize those of existing works that consider variational approximations of intractable Gibbs posteriors \cite{alquier2016properties,cottet20181}. From now on, we consider only $Q$-functions parameterized by weights $\bm{w}$ and assume them to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.

>>>>

\begin{abstract}
We consider the problem of transferring of value functions in reinforcement learning. We propose an approach that uses the given source tasks to learn a prior distribution over optimal value functions and provide an efficient variational approximation of the corresponding posterior in a new target task. We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures. We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.\todo{Say something more about the advantages of our method}
\end{abstract}

@@

%\subsection{Variational Inference}
%
%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
%\begin{equation}\label{eq:bayes}
%p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
%\end{equation}
%is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq. \eqref{eq:bayes}. The main intuition behind variational inference~\cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$. The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t. $p$:
%\begin{equation}
%\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
%\end{equation}
%It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
%\begin{equation}
%\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
%\end{equation}
%Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.

@@

Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve. Then, we can compute the posterior distribution over weights given such dataset by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$. Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$. In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions to get tractable posteriors. However, in our transfer settings, all distributions involved depend on the family of tasks under consideration and making such assumptions is likely to limit the applicability to specific problems. Thus, we take a different approach to derive a more general, but still well-grounded, solution. Recall that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$. Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
\begin{equation}\label{eq:gibbs}
q(\bm{w}) = \frac{e^{-\Lambda\norm{B_{\bm{w}}}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B_{\bm{w}'}}_D^2}p(d\bm{w}')},
\end{equation}
for some parameter $\Lambda > 0$. \todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$. Notice that, whenever the term $e^{-\Lambda\norm{B_{\bm{w}}}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior. Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models. Thus, we propose a variational approximation $q_{\bm{\xi}}$ by considering a simpler family of distributions parameterized by $\bm{\xi} \in \Xi$. Then, our problem reduces to finding the variational parameters $\bm{\xi}$ such that $q_{\bm{\xi}}$ minimizes the Kullback-Leibler (KL) divergence w.r.t. the Gibbs posterior $q$. From the theory of variational inference (e.g., \cite{blei2017variational}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
\begin{align} \label{eq:elbo}
\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
\end{align}
The approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term). Assuming that we can compute the gradients of \eqref{eq:elbo} w.r.t. the variational parameters $\bm{\xi}$, our objective can be optimized using any stochastic optimization algorithm, as shown in the next subsections.

@@

We now restrict to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement. We assume that optimal $Q$-functions (or better, their weights) follow a multivariate Gaussian distribution. That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite). Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$. To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead. In this case, deriving the gradient of the objective is very simple. Both the KL between two multivariate Gaussians and its gradients have a simple closed-form expression. The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}). Although these results are well-known in the literature, we report them in App. \ref{} to have a more self-contained description.

@@

From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t. $\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t. $\bm{w}$. Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator. This issue rarely is a problem since typical value-based algorithms are semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}). However, our transfer settings are quite different from common RL. In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum and aims only to adapt the weights in some direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the target task. Unfortunately, this property does not hold for most semi-gradient algorithms. Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching an optimum, and require many tricks and tuning to work well \cite{schaul2015prioritized,van2016deep}. This property is clearly undesirable in our case, as we only aim at adapting already good solutions. Thus, we consider using a residual gradient algorithm \cite{baird1995residual}. To differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
\begin{equation}
\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
\end{equation}
where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions. The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}. Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t. the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable w.r.t. $\bm{w}$. Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart. \cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence. This projection is obtained by including a parameter $\psi\in[0,1]$ in the TD error gradient:
\begin{equation}
\nabla_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right),
\end{equation}
where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$. Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$). A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee convergence).

@@

Our approach is mostly related to \cite{lazaric2010bayesian}. Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves the importance of capturing more complicated task distributions again. In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over MDPs. unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it. However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability. On the contrary, our approach can handle high-dimensional tasks. In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks. Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.\todo{More comments about HiP-MDPs? Should we discuss more related works?}

@@

@@

Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$. Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}. Thus, we can write:

@@

\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}

@@

\begin{lemma}
Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively. Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$. Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
\begin{equation}
\norm{Q - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
\end{equation}
\end{lemma}
\begin{proof}
First notice that:
\begin{align*}
\norm{Q - Q^*} =\ & \norm{Q + TQ - TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \norm{TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \gamma\norm{Q - Q^*}\\ =\ & \norm{B(Q)} + \gamma\norm{Q - Q^*}
\end{align*}
which implies that:
\begin{align*}
\norm{Q - Q^*} \leq\ \frac{1}{1-\gamma}\norm{B(Q)}
\end{align*}
Then we can write:
\begin{align*}
P\left( \norm{Q - Q^*} > \epsilon \right) \leq P\left(\norm{B(Q)} > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
\end{align*}
Settings the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
\end{proof}

\begin{corollary}\label{cor:diff-q}
Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively. Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$. Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
\begin{equation}
\norm{Q - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
\end{equation}
\end{corollary}
